Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-12-19 MS_revised.tex
removing BAMM

We analyzed our MCC tree in the Bayesian software BAMM in order to
contrast the results found by MEDUSA and MultiMEDUSA. BAMM (Bayesian
analysis of macroevolutionary mixtures) \cite{rabosky2014} is a software that fits
several models of speciation and extinction. The best model can be
selected by comparison of Bayes Factors.

@@

We contrasted these results with those obtained from analyzing the data
in the software BAMM \cite{rabosky2014}. We found that the best model (best
configuration) estimated 2 diversification shifts in our MCC tree
(posterior probability = 0.79) for the Ithomiini and Satyrini (Fig. S1).
Bayes factor (BF) values strongly favored this model in comparison with
a constant rate model (no diversification shifts, BF \(>\) 1,884).

@@

The results from BAMM recovered only two significant shifts in our MCC
tree as this method seems to be much more conservative than the MEDUSA
approach. One of these shifts is the Satyrini clade. MEDUSA estimated
its parent node as significant shift in only a few trees from the
posterior distribution. Thus, it might be important to take into account
phylogenetic uncertainty in BAMM as well.

@@

{\textbf{Figure S1.}} Best diversification model as estimated by BAMM.
Two diversification shifts were recovered (Ithomiini and Satyrini). The
MEDUSA analysis found a diversification shifts in Satyrinae (the parent
node of Satyini).

{\textbf{Figure S2.}} Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.

{\textbf{Figure S3.}} BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

{\textbf{Figure S4.}} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

{\textbf{Figure S5.}} Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

{\textbf{Figure S6.}} BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants. Speciation and net
diversification rates are similar.

>>>>

@@

@@

@@

{\textbf{Figure S1.}} Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.

{\textbf{Figure S2.}} BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

{\textbf{Figure S3.}} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

{\textbf{Figure S4.}} Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

{\textbf{Figure S5.}} BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants. Speciation and net
diversification rates are similar.
